---
title: "Quarto template"
author: "Jozef (ultimate nerd) Rivest"
date: "october 16, 2025" 
date-format: long # To have the date as text instead of 10-16-2025
format: 
  pdf:
    documentclass: article # To have the same beautiful output as overleaf
    fontsize: 12pt # To change the fontsize
    geometry: # To adjust the margins
      - margin=1in
    keep-tex: true # To keep the .tex code

bibliography: references.bib # The bib files for the citations
---

This document provides a short introduction to Quarto. A few tips are highlighted all along the file. If you have any questions, feel free to ask me, or to refer to [Quarto guide](https://quarto.org/docs/guide/). The best way to learn from it is either to try to replicate some parts, or to change some parts and see how the output changed.

Have fun!

{{< pagebreak>}}

# First level header

[@svolik2012] <!-- This is parentheses citation -->

@svolik2012 <!-- This is a text citation -->

```{r}
dat <- mtcars

hist(dat$cyl)
```

```{r}
library(tinytable) # Super nice package for table!

tt(dat)
```

You can insert math equations the same way you would do in \LaTeX. Either with the double dollar sign, or using `begin{equation} end{equation}` in a \LaTeX chunk.

$$
P(A|B) = \frac{P(B|A)P(A)}{P(B|A)P(A) + P(B|A^c)P(A^c)}
$$

```{=tex}
\begin{equation}
P(A|B) = \frac{P(B|A)P(A)}{P(B|A)P(A) + P(B|A^c)P(A^c)}
\end{equation}
```



{{< pagebreak >}}

# References

::: {#refs}
:::

{{< pagebreak >}}

# Appendix

Sometimes, packages print errors, messages, and warnings. To silence them, you can add the following in the code chunk (see the second code chunk below)

```{r}

library(tidyverse)
```

```{r}
#| message: false 
#| error: false
#| warning: false

library(tidyverse)
```

{{< pagebreak >}}

# Appendix 2

If you want to hide the code, you can add `echo: false` to the code chunk:

```{r}
#| echo: false

tt(dat)
```
